An Example Article

### 2024-10-10 amsart-en/amsart-journal.tex
update

\keywords{Keyword 1, keyword 2, error analysis}

@@

\begin{abstract}
This is an example \LaTeX\ article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.
\end{abstract}

@@

In this paper we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
  &\, u(x,y,t) = g(t), \quad \text{on } ~ \partial \Omega, \\
  &\, u(x,y,0)=\varphi(x, y), \quad \text{on } ~\Omega.
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

This is an example of quoting an equation \eqref{eq:mulequ}.

@@

This is a equation in appendix.
\begin{equation}\label{eq:abc}
  a^2+b^2=c^2.
\end{equation}

>>>>

\keywords{Academic article, example, \LaTeX{} template}

@@

\begin{abstract}
This is an example \LaTeX{} article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references, equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.
\end{abstract}

@@

In this paper, we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
  & u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega \times \mathcal{T},, \\
  & u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega,
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

This is an example of referencing the equation \eqref{eq:mulequ}.

@@

This is an equation in the appendix.
\begin{equation}\label{eq:abc}
  a^2+b^2=c^2.
\end{equation}

### 2024-10-10 article-en/article-temp-info.tex
update

@@

% Information for title and author
\title{An Example Article\tfootnote{This is a title footnote}}

@@

\author[1]{Author A}
\author[2]{Author B}
\author[1,\cormark]{Author C}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
\cortext{Corresponding author. Email address: \texttt{xyz@math.univ.edu}}

@@

\date{Date: \today}

@@

\begin{abstract}
This is an example \LaTeX\ article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.

\medskip
\noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods

@@

@@

In this paper we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
  &\, u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega, \\
  &\, u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega.
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

This is an example of quoting an equation \eqref{eq:mulequ}.

@@

This is a equation in appendix.
\begin{equation}\label{eq:A1}
  a^2+b^2=c^2.
\end{equation}

>>>>

% package for line number
%\usepackage[pagewise,mathlines]{lineno}
%\linenumbers
%\modulolinenumbers[5]

@@

% Full Title of the paper
\title{Academic Article Template for Manuscript or Preprint\tfootnote{This is a title footnote}}

@@

% Authors and their affiliations
\author[1]{Author A}
\author[2]{Author B}
\author[1,\cormark]{Author C}
\affil[1]{Department of Mathematics, \LaTeX{} University}
\affil[2]{Department of Mechanical Engineering, \LaTeX{} University}
\cortext{Corresponding author. Email address: \texttt{xyz@math.univ.edu}}

@@

% Date is editable
\date{Date: \today}

@@

\begin{abstract}
This is an example \LaTeX{} article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references, equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.

\medskip
\noindent{\bfseries Keywords}: Academic article, Example, \LaTeX{} template

@@

%%%%%%%%%% main body %%%%%%%%%%

@@

In this paper, we present a new method for solving the model equation
\begin{equation}\label{eq:mulequ}
\left\{\begin{aligned}
  & \partial_{t} u-\varepsilon^{2} \Delta u+u^{3}-u=0, \quad \text{in} ~\Omega\times\mathcal{T}, \\
  & u(x,y,t) = g(t), \quad \text{on} ~ \partial \Omega \times \mathcal{T},, \\
  & u(x,y,0)=\varphi(x, y), \quad \text{on} ~\Omega,
\end{aligned}\right.
\end{equation}
where $\varepsilon$ is a small parameter.

This is an example of referencing the equation \eqref{eq:mulequ}.

@@

This is an equation in the appendix.
\begin{equation}\label{eq:A1}
  a^2+b^2=c^2.
\end{equation}

### 2024-10-10 article-en/article-temp.tex
update

\author{
  Author A\thanks{Department of Computer Science, \LaTeX\ University}~,
  Author B\thanks{Department of Mathematics, \LaTeX\ University}~,
  and
  Author C\thanks{Department of Mechanical Engineering, \LaTeX\ University}
}

>>>>

\author{
  Author A\thanks{Department of Computer Science, \LaTeX{} University}~,
  Author B\thanks{Department of Mathematics, \LaTeX{} University}~,
  and
  Author C\thanks{Department of Mechanical Engineering, \LaTeX{} University}
}

### 2024-10-10 article-en/article-temp2.tex
update

\author{
  Author A \\
  {\itshape Department of Computer Science, \LaTeX\ University} \\
  \and
  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
  {\itshape Department of Mathematics, \LaTeX\ University} \\
  \and
  Author C\thanks{This author was supported in part by NSFC Grant No. 12345678.} \\
  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
}

>>>>

\author{
  Author A \\
  {\itshape Department of Computer Science, \LaTeX{} University} \\
  \and
  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
  {\itshape Department of Mathematics, \LaTeX{} University} \\
  \and
  Author C\thanks{This author was supported in part by NSFC Grant No. 12345678.} \\
  {\itshape Department of Mechanical Engineering, \LaTeX{} University} \\
}
